Title Goes Here

### 2024-04-05 analysis/paper/paper.qmd

fig_how_many_jobs_per_year <- 
ggplot(jobdata) +
  aes(year_ad_posted) +
  geom_bar() +
  scale_x_discrete(name = "Academic Year") +
  ylab("Number of\ntenure track job ads") +
  theme_minimal(base_size = 14)

@@

years_to_2019 <- map_chr(2013:2019, ~str_glue('{.x}-{.x +1}'))
years_after_2020 <- map_chr(2020:2022, ~str_glue('{.x}-{.x +1}'))
# though it seems to start at 2007-8: https://academicjobs.fandom.com/wiki/Archaeology_07-08

@@

# draw plot
fig_ratio_tt_2_ntt_jobs_per_year <- 
  ggplot(count_of_tt_jobs_per_year_from_our_form) +
  aes(year, 
      group = 1,
      ratio_tt_2_ntt) +
  geom_line(linewidth = 2) +
  geom_hline(yintercept = 1,
             colour = "red") +
  annotate("text", 
           x = 3, 
           y = 1.3, 
           label = "1:1 ratio",
           colour = "red") +
  labs(y = "Ratio of tenure-track to\nnon-tenure track and other",
       x = "") +
  theme_minimal(base_size = 14) +
   guides(x = "none")

@@

```{r}
# save these three plots as one set
library(cowplot)
plot_grid(
  fig_ratio_tt_2_ntt_jobs_per_year,
  fig_prop_by_job_title_per_year,
  fig_how_many_jobs_per_year,
  ncol = 1,
  align = "hv",
  axis = "lr"
)

>>>>

fig_how_many_jobs_per_year <- 
ggplot(jobdata) +
  aes(year_ad_posted) +
  geom_bar() +
  scale_x_discrete(name = "Academic Year") +
  ylab("Number of\ntenure track job ads") +
  theme_minimal(base_size = 14) +
  guides(x = "none")

@@

years_to_2019 <- map_chr(2012:2019, ~str_glue('{.x}-{.x +1}'))
years_after_2020 <- map_chr(2020:2022, ~str_glue('{.x}-{.x +1}'))
# though it seems to start at 2007-8: https://academicjobs.fandom.com/wiki/Archaeology_07-08

@@

# draw plot
fig_ratio_tt_2_ntt_jobs_per_year <- 
  ggplot(count_of_tt_jobs_per_year_from_our_form) +
  aes(year, 
      group = 1,
      ratio_tt_2_ntt) +
  geom_line(linewidth = 2) +
  geom_hline(yintercept = 1,
             colour = "red") +
  annotate("text", 
           x = 3, 
           y = 1.3, 
           label = "1:1 ratio",
           colour = "red") +
  labs(y = "Ratio of tenure-track to\nnon-tenure track and other",
       x = "") +
  theme_minimal(base_size = 14) #+
   #guides(x = "none")

@@

```{r}
# save these three plots as one set
library(cowplot)
plot_grid(
  fig_how_many_jobs_per_year,
  fig_prop_by_job_title_per_year,
  fig_ratio_tt_2_ntt_jobs_per_year,

  ncol = 1,
  align = "hv",
  axis = "lr",
  labels = "AUTO"
)
